### 2021-04-15 papers/SYRCoSE/overview.tex
fix: grammar
clarify perks of using decidable thigs

We build our mechanisation on top of the \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
using the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq system.
We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of the \ssreflect.

@@

To achieve better automation one is encouraged 
to use \emph{decidable} and \emph{computable} procedures
whenever possible.
For example, in the context of our library, 
we encode the binary relations of the event structures
as decidable \texttt{bool}-valued relations, 
\ie $\caOrd, \cfRel : E \fun E \fun \texttt{bool}$,
as opposed to \emph{propositional} 
relations of type $E \fun E \fun \texttt{Prop}$.

>>>>

We build our mechanisation on top of the \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
using the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq system.
We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of \ssreflect.

@@

To achieve better automation and e.g. get \emph{proof irrelevance}
automatically, one is encouraged
to use \emph{decidable} and \emph{computable} procedures
whenever possible.
For example, in the context of our library, 
we encode the binary relations of the event structures
as decidable \texttt{bool}-valued relations, 
\ie $\caOrd, \cfRel : E \fun E \fun \texttt{bool}$,
as opposed to \emph{propositional} 
relations of type $E \fun E \fun \texttt{Prop}$.
